Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
paragraph regarding HTER measure

\begin{itemize}
\item Evaluation of evaluation measures
  \begin{itemize}
  \item correlation vs. human fluency/adequacy 
  \item correlation vs. human-in-the-loop measures (HTER)
  \end{itemize}
\item one challenge of metric-evaluation: underlying doc difficulty 
  \begin{itemize}
  \item describe mean-subtraction
  \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
\item \sout{Evaluation of evaluation measures}
  \begin{itemize}
  \item \sout{correlation vs. human fluency/adequacy }
  \item \sout{correlation vs. human-in-the-loop measures (HTER)}
  \end{itemize}
\end{itemize}

We may evaluate automatic MT measures in a variety of ways. Some
\cite{banerjee05meteor,liu05syntaxformteval,owczarzak07labelleddepseval}
have evaluated their success by comparing the measure to human
judgments of fluency and adequacy.  In other work,
e.g. \newcite{snover06ter}, measures are evaluated by comparison to
human-targeted TER (HTER), a distance to a human-revised reference
that uses wording closer to the MT system choices (keeping the
original meaning) that is intended to measure the post-editing work
required after translation.  In this paper, we pursue both kinds of
evaluation.

\begin{itemize}
\item one challenge of metric-evaluation: underlying doc difficulty 
  \begin{itemize}
  \item describe mean-subtraction
  \end{itemize}
\end{itemize}
